---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wapoposh

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of wapoposh from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("parmsam/wapoposh")
```

## Example

This is a basic example which shows you how to interact with the dataset:

```{r example, message = FALSE}
library(wapoposh)
library(dplyr)
# basic example code
tail(policeshootings, 4)
# get latest data
latest <- latest_data()
tail(latest, 4)
```

```{r glimpse, message = FALSE}
glimpse(policeshootings)
```

## Note

The data was originally published under an Attribution-NonCommercial-ShareAlike 4.0 International (CC BY-NC-SA 4.0) license.

## Credit

Credit goes to the Washington Post research and reporting/database development team for compiling and sharing the dataset on their [Github repo](https://github.com/washingtonpost/data-police-shootings).
